---
title: "P8105 Homework 3"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

```{r}
data("instacart")
```

The "instacart" dataset contains 1384617 obsevations in total and each row in the dataset represents a product from an order. There are 15 variables in this dataset. The order_id variable is the order identifier. The product_id variable is the product identifier. The add_to cart_order variable represents the order in which each product was added to cart. The reordered variable is 1 if this prodcut has been ordered by this user in the past and 0 otherwise. The user_id variable is the customer identifier. The eval_set variable represents  which evaluation set this order belongs in. The order_number variable is the order sequence number for this user (1 = first,  n = nth). The order_dow variable represents the day of the week on which the order was placed. The order_hour_of_day variable is the hour of the day on which the order was placed. The days_since_prior_order represents days since the last order, capped at 30, NA if order_number = 1. The product_name variable is the name of the product. The aisle_id variable is the aisle identifier. The department_id variable is the department identifier. The aisle variable represents the name of the aisle the product is in. The department variable represents the name of the department the product is in.

```{r}
instacart %>%
  group_by(aisle) %>%
  summarize(total = n()) %>%
  arrange(desc(total))
```

From the table above, we can see that there are 134 aisles and the top 10 aisles that most items are ordered from include fresh vegetables, fresh fruits, packaged vegetable fruits, yogurt, packaged cheese, water seltzer sparkling water, milk, chips pretzels, soy lactosefree, and bread.

```{r}
instacart %>%
  group_by(aisle) %>%
  summarize(total = n()) %>%
  arrange(desc(total)) %>%
  filter(total > 10000) %>%
  mutate(aisle = fct_reorder(aisle, total)) %>%
  ggplot(aes(x = total, y = aisle)) + geom_point() + labs(title = "Top 39 Aisles With Most Items Ordered", xlab = "Number of items", ylab = "Aisle") + scale_x_continuous(breaks = seq(from = 0, to = 160000, by = 20000))
```

The plot above shows the number of items ordered in each aisle.

```{r}
instacart %>%
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%
  group_by(aisle, product_name) %>%
  summarize(order_times = n()) %>%
  arrange(desc(order_times)) %>%
  mutate(rank = min_rank(desc(order_times))) %>%
  filter(rank <= 3) %>%
  knitr::kable()
```

The table above shows the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables along with the number of times ordered.



